\documentclass[a4paper]{article}

\usepackage{titlesec}  % reformatting titles
\usepackage{titling}  % customize maketitle
\usepackage{indentfirst}  % indent first word of every paragraph
\usepackage[none]{hyphenat}  % prevent hyphenation in the entire document by setting the hyphenation languages to none
\usepackage[margin=0.55in]{geometry}
\usepackage{hyperref}  % for hyerlinks
\usepackage{enumitem}

% ATS friendly resume
\usepackage[T1]{fontenc}  % for font encoding
\input{glyphtounicode}

\pagenumbering{gobble}  % no page numbering

\renewcommand{\maketitle}{
	\begin{center}
		{\Huge\bfseries{\theauthor}}\\
			\vspace{0.5em}
		{
			\begin{center}
                \begin{minipage}{0.4\linewidth}
                    \large\begin{tabular}{l  l}
                        \textbf{Email:} & \href{mailto:arsanysamuel.as@gmail.com}{arsanysamuel.as@gmail.com}  \\ 
                        \textbf{Phone:} & \href{tel:+201068874670}{+20 106 887 4670}  \\
                    \end{tabular}
                \end{minipage}
                \hspace{1em}
                \begin{minipage}{0.4\linewidth}
                    \large\begin{tabular}{l  l}
                        \textbf{Linkedin:} & \href{https://linkedin.com/in/arsanysamuel}{linkedin.com/in/arsanysamuel}  \\
                        \textbf{Github:} & \href{https://github.com/arsanysamuel}{github.com/arsanysamuel}
                    \end{tabular}
                \end{minipage}
			\end{center}
		}
	\end{center}
}

\titleformat{\section}   % reformat title (titlesec)
	{\huge\bfseries}  % formatting
	{}  % numbering, default: \thesection
	{0em}  % space before the title
	{}  % text before title
	[\titlerule]  % followed by (optional)

\titleformat{\subsection}
	{\Large\bfseries}
	{\hspace{0em}$\bullet$}
	{0em}
	{\hspace{0.25em}}

\titleformat{\subsubsection}
	[runin]  % run the title with the paragraph in the same line (optional)
	{\bfseries}
	{}
	{0em}
	{}
	[:]

\titlespacing{\subsubsection}  % modify title spacing (titlesec)
	{0em}  % right spacing
	{0.25em}  % vertical spacing
	{1em}  % left spacing

\newcommand{\entry}[4]{   % new command takes 4 args, will improve with xargs package to take optional arguments later
	\begin{center}
		\begin{minipage}[c]{0.2\linewidth}  % [t] is optional positioning argument, try h,b,t,p , using text width as it's a constant width
			\vfill
			\hfill  % align to the right
			\textsc{#1}  % small caps word, # for the argument number
			\vfill
		\end{minipage}
		\hfill\vline\hfill  % vertical line in the center
		\begin{minipage}[c]{0.75\linewidth}
            \textrm{\bfseries{#2}} \\
			\textit{#3} \\
			\footnotesize{#4}
		\end{minipage}
	\end{center}
}

\newcommand{\smallentry}[2]{   % new command takes 2 args
	\begin{center}
		\begin{minipage}[c]{0.2\linewidth}  % [t] is optional positioning argument, try h,b,t,p , using text width as it's a constant width
			\vfill
			\hfill  % align to the right
			\textsc{#1}  % small caps word, # for the argument number
			\vfill
		\end{minipage}
		\hfill\vline\hfill  % line in the center
		\begin{minipage}[c]{0.75\linewidth}
			\vfill
			\textrm{#2} 
			\vfill
		\end{minipage}
	\end{center}
}

\newcommand{\blist}[1]{  % custom bullet list
    \vspace{-\topsep}
    \renewcommand\labelitemi{\tiny$\bullet$}
    \begin{itemize}[leftmargin=3.5mm, noitemsep]
        #1
    \end{itemize}
}

\newcommand{\sblist}[1]{  % custom bullet sublist
    \vspace{-\topsep}
    \renewcommand\labelitemii{\textopenbullet}
    \begin{itemize}[leftmargin=5mm, noitemsep]
        #1
    \end{itemize}
}

\title{R\'esum\'e}
\author{Arsany Samuel}

\begin{document}
	\maketitle

	\section{Experience}
        \entry{Mar 2023 - Present}
            {DevOps Engineer}
            {\href{https://www.noury.ch/}{Noury AG.} (Switzerland - Remote)}
            {
                \blist{
                    \item \textbf{DevOps Engineer (Jul 2025 - Present)}
                    \sblist{
                        \item{Architected and managed secure cloud infrastructure on GCP using Terraform (IaC),
                            optimizing resource allocation, enforcing security best practices, and reducing monthly cloud costs by 50-60\%.}
                        \item{Containerized applications with Docker, orchestrating scalable deployments via Kubernetes and Helm to ensure highly available systems.}
                        \item{Engineered CI/CD workflows using Bitbucket Pipelines for multiple projects,
                            ensuring short release cycle, fast and reliable deployments.}
                        \item{Streamlined version control workflows and local environment setups,
                            significantly enhancing the developer experience and boosting team deployment frequency.}
                        \item{Implemented comprehensive observability and monitoring systems, improving incident response times and maintaining service health.}
                    }
                    \item \textbf{Software Developer / DevOps Engineer (Apr 2023 - Jun 2025)}
                    \sblist{

                        \item{Designed and implemented a robust backend REST API for the Noury consumer mobile app using Django Rest Framework (DRF),
                            ensuring scalable and seamless data integrations.}
                        \item{Engineered a custom ERP solution using Frappe/ERPNext,
                            synchronizing multiple third-party data sources and APIs to improve internal operational efficiency.}
                        \item{Led the delivery of data pipelines, automated data analysis and AI integrations that provide business insights to the Noury team.}
                        \item{Mentored junior engineers and interns on technical best practices,
                            directly accelerating project delivery timelines and fostering professional growth.}
                    }
                }
            }
        \entry{Nov 2024 - May 2025}
            {DevOps Engineer}
            {\href{https://yourstore.ch/}{YourStore Systems AG.} (Switzerland - Contract)}
            {
                \blist{
                    \item Led the backend engineering team to architect a robust API and modular ERP system using Python and
                        Frappe framework with ERPNext for an unattended retail platform service.
                    \item Architected and provisioned scalable GCP infrastructure via Terraform (IaC), orchestrating Docker containers with Kubernetes and Helm.
                    \item Engineered automated CI/CD workflows with GitHub Actions, accelerating feature release cycles and reducing deployment time
                        without compromising reliability.
                    \item Accelerated time-to-market by successfully launching 3 client businesses (unmanned stores) on the new platform
                        within the first 6 months of development.
                }
            }
        \entry{Nov 2019 - Feb 2023}
            {Software Developer}
            {Freelance (Self-Employed)}
            {
                \blist{
                    \item Providing prototyping and software solution services that integrates well with hardware solutions using image processing,
                        desktop application frameworks, SQL databases.
                }
            }
        \entry{Jun 2021 - Mar 2022}
            {Software \& Mechatronics Engineer}
            {Specialist Company for Engineering Solutions. (Alexandria, Egypt)}
            {
                \blist{
                    \item Developed desktop applications for an automated warehouse robotic solution that uses machine vision for product picking and sorting,
                        synchronizing with systems to ensure data integrity.
                    \item Designed, implemented and tested prototypes of custom solutions for Building Management Systems,
                        adding extra safety features to the existing systems, including mechanical, electrical and PCB layout designs.
                }
            }

	\section{Skills}
        \subsection{Software}
			\subsubsection{Programming Languages}
			Python, Bash/Shell scripting, Javascript, SQL %, C, C++
            \subsubsection{DevOps \& Cloud Tools}
            Linux, Git, Docker, Kubernetes, Terraform, Helm, GitHub Actions, Bitbucket Pipelines, GCP, AWS
            \subsubsection{Development Frameworks}
            Django, DRF, FastAPI, Flask, Frappe/ERPNext
			\subsubsection{Markup Languages}
			Markdown, {\LaTeX}, HTML/CSS.
			%\subsubsection{Other Tools}
			%SolidWorks, EagleCAD, KiCAD, Circuit design, Microcontrollers

		% might remove 
		%\subsection{Languages}
			%Arabic(Mother Tongue), English (Proficient).

    \section{Projects}
        \smallentry{\footnotesize{Noury Consumer App}}
            {
                \blist{
                    \item Designed and developed a scalable backend REST API using Django Rest Framework to support Noury's consumer mobile application.
                    \item Optimized CI/CD pipelines and automated deployment processes using Docker for containerization and Kubernetes for orchestration,
                        enhancing release efficiency, scalability, and minimizing downtime.
                    \item Implemented monitoring and logging strategies to maintain API performance and reliability.
                }
            }
        \smallentry{\scriptsize{Noury Resource Planning}}
            {
                \blist{
                    \item Engineered a customized ERP system using Frappe/ERPNext, designed to streamline internal operations and enhance business efficiency.
                    \item Implemented advanced data synchronization techniques to integrate multiple third-party data sources and APIs,
                        ensuring real-time updates and accurate information across systems.
                    \item Customized ERP modules and workflows to meet specific business needs,
                        including automated reporting and process automation to improve operational efficiency.
                    \item Optimized system performance and scalability, adapting the ERP solution to support growing business demands and evolving requirements.
                }
            }
        \smallentry{\footnotesize{YourStore Platform}}
            {
                \blist{
                    \item Led the backend team and contributed to the implementation of an API backend and ERP system for a reliable,
                        modular platform for unattended retail.
                    \item Built a cloud infrastructure on GCP using IaC, CI/CD, containerization and orchestration config for the whole system.
                    \item Launched 3 successful client projects (unmanned stores) on new platform in first 6 months.
                }
            }

        % Try to add some data analysis/engineering and cloud projects

        %\smallentry{\footnotesize{Irrigation Controller}}
            %{
                %\blist{
                    %\item Engineered a microprocessor-based system with advanced algorithms,
                        %integrating data from wireless weather stations and sensors to optimize watering needs.
                    %\item Developed a customizable user interface, including kiosk, mobile app, and web portal,
                        %and implemented both wired and wireless communication methods.
                    %\item Integrated a computer vision application to monitor field images, track irrigation processes,
                        %and maintain plant health, improving overall system efficiency.
                %}
            %}
        %\smallentry{Robotic Arm}
            %{
                %\blist{
                    %\item Engineered and manufactured a robotic arm with 6 degrees of freedom for automated agricultural product collection,
                        %equipped with an pneumatic powered manipulator and integrated system components to enhance efficiency in harvesting operations.
                    %\item Implemented machine learning and computer vision to accurately identify and differentiate fruits and drive the arm to collect them.
                %}
            %}
        %\smallentry{Vortex ROV}
            %{
                %\blist{
                    %\item Contributed in the design and fabrication of a remotely operated underwater vehicle featuring two manipulators and a quad camera vision system.
                    %\item Programmed the ROV for advanced control and operation for the MATE ROV Competition 2019 and Underwater Sea Challenges 2020.
                    %\item Integrated the vehicle's components to ensure effective performance in harsh underwater environments.
                %}
            %}

	\section{Training and Certifications}
		\entry{February 2026}
			{Solutions Architect Associate}
			{Amazon Web Services}
			{\url{credly.com/badges/c1d8dec5-eb48-4f56-8ba7-40b631c2d7ca/public_url}}
		\entry{February 2026}
			{Professional Cloud Architect}
			{Google Cloud Platform}
			{\url{credly.com/badges/7ef1d890-0bdd-4124-b552-d74fefa5ebbb/public_url}}
		\entry{June 2025}
			{Associate Cloud Engineer}
			{Google Cloud Platform}
			{\url{credly.com/badges/515940bf-b2cd-4879-9306-2c6c4f411098/public_url}}
		\entry{April 2023}
			{Agile Explorer}
			{IBM}
			{\url{credly.com/badges/7b1b3f1f-edc3-4ffd-9328-7c55b4078b57/public_url}}
		\entry{March 2023}
			{Thinking and Creating with Code}
			{EPFL Extension School}
			{\url{learn.extensionschool.ch/verify/VqOzbOAyD9pl}}
		\entry{September 2022}
			{CS50x}
			{Harvard University}
			{\url{certificates.cs50.io/fe015e39-3d8e-48ad-a13b-4177ec41e108.pdf}}
		\entry{July 2021}
			{CSWE: Certified SolidWorks Expert - Mechanical Design.}
			{Dassault Systèmes}
			{C-6NMDPAQ9UE}

	\section{Education}
		\entry{2016 - 2021}
			{B.S.E. in Agricultural Engineering}
			{Faculty of Agriculture, Alexandria University }

\end{document}
